---
title: "Estimating Bias Induced by Sample Selection: A Comparison of Five Weighting Schemes for a Highly Selected Sample"
subtitle: "Graphical Comparisons of Weighting Schemes"
author: "Audrey R Murchland (edited by ERM 1/19/2020) (edited by KVD 2/14/2022)"
date: "2/4/2019"
output: 
  html_document:
    theme: flatly
    toc: TRUE
    toc_float: TRUE
    toc_depth: 3
File  name: Creating_Figures_Graphs_25May2022.Rmd

---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE)
```

```{r Pacman statement}
if (!require("pacman")) install.packages("pacman", repos='http://cran.us.r-project.org'); library(pacman)
p_load("tidyverse", "knitr", "kableExtra", "magrittr", "reshape2", "here", "sas7bdat", "ggplot2", "dplyr", "kableExtra", "tables", "huxtable", "RColorBrewer", "latex2exp","scales", "openxlsx", "grid", "gtable", "gridExtra", "tableone", "Tabstat", "survey")
options(digits = 3)
options(scipen = 999)
```
#Audrey's To Dos:
-

```{r Pulling data}
#path_to_box: Updating the path here will update everything throughout the script

# #EHL's path
 path_to_box <- "C:/Users/ehlarson/Box/"

#CS path
# path_to_box <- "/Users/crystalshaw/Library/CloudStorage/Box-Box/JZ_CS/"

results <- read.csv(paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Output/all_weights052522.csv")) %>% dplyr::select(-X)
results$model2 <- factor(results$model2,levels = c("CHIS Weighted", "ADC super learner", "ADC SL GBM", "ADC Logistic","ADC Raked","ADC Unweighted" ))
scaleFUN <- function(x) sprintf("%.2f", x)
results$Labels[results$model2=="ADC Unweighted"] <- "ADC - equal weights" 
results$Labels[results$model2=="ADC SL GBM"] <- "ADC - sIOSW,\nalgorithm: GBM" 
results$Labels[results$model2=="ADC Logistic"] <- "ADC - sIOSW,\nalgorithm: logistic regression" 
results$Labels[results$model2=="ADC Raked"] <- "ADC - raking weights" 
results$Labels[results$model2=="ADC super learner"] <- "ADC - sIOSW,\nalgorithm: super learner" 
results$Labels[results$model2=="CHIS Weighted"] <- "CHIS*"
results$Labels <- factor(results$Labels, levels = c("ADC - equal weights", "ADC - raking weights", "ADC - sIOSW,\nalgorithm: logistic regression" ,"ADC - sIOSW,\nalgorithm: GBM" , "ADC - sIOSW,\nalgorithm: super learner" , "CHIS*" ))

#aTable 8 no longer included in the manuscript
OddsRatios <- results %>% filter(Statistic=='Odds Ratio', Stdpop == "stdchis") %>% mutate(Group2 = case_when(Group=="Black" ~ "Black vs. White",
                                                                                                             Group=="Latino" ~ "Latino vs. White"))
write.csv(OddsRatios, file=paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Final graphics/Manuscript_aTables8_052522.csv"))
PrevRatios <- results %>% filter(Statistic=='Rel Risk', Stdpop == "stdchis") %>% mutate(Group2 = case_when(Group=="Black" ~ "Black vs. White",
                                                                                                           Group=="Latino" ~ "Latino vs. White"))
write.csv(PrevRatios, file=paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Final graphics/Manuscript_aTables6_052522.csv"))
```
#Comparisons of Applied Weighting Schemes

##Odds Ratios
<br>
<br>
```{r Odds Ratio Plots, echo=FALSE, fig.align="center", fig.width=7, fig.height=5}
OddsRatios$textY = 0.60
OddsRatios_m <- OddsRatios %>% mutate(LowerCL_l = ifelse(LowerCL < 0.80, 0.80, LowerCL), UpperCL_l = ifelse(UpperCL > 4.2, 4.2, UpperCL), 
                                      UpperCL_d = ifelse(UpperCL > 4.2, 4.2, NA))
or <- ggplot(OddsRatios_m, aes(x=Labels, y=Value)) + 
  geom_point(size = 10, alpha = 0.75, aes(fill=model3),colour="black", pch=21) +
  theme(aspect.ratio = 2) +
  geom_errorbar(aes(ymin=LowerCL_l, ymax=UpperCL_l),
                size=.8,    # Thinner lines
                width=.2, 
                position=position_dodge(.9)) +
  labs(x="", y="Estimated Odds Ratio (95% CI)") + 
  ggtitle("Hypertension Odds Ratios based on each weighting scheme") +
  scale_y_continuous(trans = "log", breaks=c(0.8,1.0,1.2,1.5,1.8,2.2,2.7,3.3,4.1), labels=scaleFUN, limit=c(0.8,4.2),expand=c(0,0), minor_breaks=NULL) +
  guides(fill=FALSE) +
  scale_fill_manual(values=c("G1"="white", "G2"="red1", "G3"="turquoise1","G4"="gold1","G6"="orchid1","G5"="black")) +
  theme_bw() +
  geom_text(aes(label=scaleFUN(Value)),hjust=.50, vjust=-1.25, size=6) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=17, color="black"), plot.title = element_text(hjust=0.5), axis.text.y=element_text(size=20, color="black")) +
  geom_hline(yintercept=1) + 
  scale_x_discrete(limits=rev(levels(OddsRatios$Labels))) +
  coord_flip() + 
  theme(panel.spacing= unit(3.0, "lines"))+
  theme(axis.text.y = element_text(hjust = 0)) + 
  facet_wrap(~ Group2) +
  # geom_segment(aes(x = 2, xend = 2, y = Value, yend = UpperCL_d), arrow = arrow(length = unit(0.5, "cm"))) + # SL arrow Black
  geom_segment(aes(x = 3, xend = 3, y = Value, yend = UpperCL_d), arrow = arrow(length = unit(0.5, "cm"))) + # GBM arrow Black
  geom_segment(aes(x = 4, xend = 4, y = Value, yend = UpperCL_d), arrow = arrow(length = unit(0.5, "cm"))) #log arrow Black

or2 <- or + theme(strip.text = element_text(size=23),
                  plot.title = element_text(color="black", size=25, face="bold"),
                  axis.title.x = element_text(color="black", size=23, vjust=-3.0),
                  axis.title.y = element_text(color="black", size=16),
                  plot.margin = margin(1,1,1,.1,"cm"), plot.background = element_rect(fill="white")
)
plot(or2)
aspect_ratio <- 1.5
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/OR_052522.png'), plot=or2, height=7,width = 10 * aspect_ratio )
```
<br>
<br>

##Prevalence Ratios
<br>
<br>
```{r Prevalence Ratio Plots, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
PrevRatios$textY = 0.90
pr <- ggplot(PrevRatios, aes(x=Labels, y=Value)) + 
  geom_point(size = 10, alpha = 0.75, aes(fill=model3),colour="black", pch=21)+
  theme(aspect.ratio = 2) +
  geom_errorbar(aes(ymin=LowerCL, ymax=UpperCL),
                size=.8,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x="", y="Estimated Prevalence Ratio (95% CI)") +
  ggtitle("Hypertension Prevalence Ratios based on each weighting scheme") +
  scale_y_continuous(trans = "log", breaks=c(0.8,1.0,1.2,1.5,1.8,2.2), labels=scaleFUN, limit=c(0.8,2.2),expand=c(0,0), minor_breaks=NULL) +
  guides(fill=FALSE) +
  scale_fill_manual(values=c("G1"="white", "G2"="red1", "G3"="turquoise1","G4"="gold1","G6"="orchid1","G5"="black")) +
  theme_bw() +
  geom_text(aes(label=scaleFUN(Value)),hjust=.50, vjust=-1.25, size=6) +  
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=17, color="black"), plot.title = element_text(hjust=0.5), axis.text.y=element_text(size=20, color="black")) +
  geom_hline(yintercept=1) + 
  scale_x_discrete(limits=rev(levels(PrevRatios$Labels))) +
  coord_flip() + 
  theme(panel.spacing= unit(3.0, "lines"))+
  theme(axis.text.y = element_text(hjust = 0)) + 
  facet_wrap(~ Group2) 
# geom_segment(aes(x = 2, xend = 2, y = Value, yend = UpperCL_d), arrow = arrow(length = unit(0.5, "cm")))+
# geom_segment(aes(x = 4, xend = 4, y = Value, yend = UpperCL_d), arrow = arrow(length = unit(0.5, "cm")))
pr2 <- pr + theme(strip.text = element_text(size=23),
                  plot.title = element_text(color="black", size=25, face="bold"),
                  axis.title.x = element_text(color="black", size=23, vjust=-3.0),
                  axis.title.y = element_text(color="black", size=16),
                  plot.margin = margin(1,1,1,.1,"cm"), plot.background = element_rect(fill = "white")
)
plot(pr2)
aspect_ratio <- 1.5
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/PR_052522.png'), plot=pr2,  height=7,width = 10 * aspect_ratio )
```
<br>
<br>

##Prevalence Differences
```{r Prev Diff Data}
# resultspd <- read.sas7bdat("/Users/audreymurchland/Box Sync/UCD Health Cognition/Data/ADC-CHIS_DATA/Applied_Weights/all_weights092219.sas7bdat")
# resultspd$model2 <- factor(resultspd$model2,levels = c("CHIS Weighted", "ADC super learner", "ADC SL GBM", "ADC Logistic","ADC Raked","ADC Unweighted" ))
# scaleFUN <- function(x) sprintf("%.1f", x)
# resultspd$Labels[resultspd$model2=="ADC Unweighted"] <- "ADC - equal weights" 
# resultspd$Labels[resultspd$model2=="ADC SL GBM"] <- "ADC - sIOSW,\nalgorithm: GBM" 
# resultspd$Labels[resultspd$model2=="ADC Logistic"] <- "ADC - sIOSW,\nalgorithm: logistic regression" 
# resultspd$Labels[resultspd$model2=="ADC Raked"] <- "ADC - raking weights" 
# resultspd$Labels[resultspd$model2=="ADC super learner"] <- "ADC - sIOSW,\nalgorithm: super learner" 
# resultspd$Labels[resultspd$model2=="CHIS Weighted"] <- "CHIS*"
# resultspd$Labels <- factor(resultspd$Labels, levels = c("ADC - equal weights", "ADC - raking weights", "ADC - sIOSW,\nalgorithm: logistic regression" ,"ADC - sIOSW,\nalgorithm: GBM" , "ADC - sIOSW,\nalgorithm: super learner" , "CHIS*" ))
# PrevDiff <- resultspd %>% filter(Statistic=='Risk Diff')
# PrevDiff$Value2 <- PrevDiff$Value*100
# PrevDiff$LowerCL2 <- PrevDiff$LowerCL*100
# PrevDiff$UpperCL2 <- PrevDiff$UpperCL*100
PrevDiff <- results %>% filter(Statistic=='Risk Diff', Stdpop == "stdchis") %>% mutate(Group2 = case_when(Group=="Black" ~ "Black vs. White",
                                                                                                          Group=="Latino" ~ "Latino vs. White"))
scaleFUN <- function(x) sprintf("%.1f", x)
write.csv(PrevDiff, file=paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Final graphics/Manuscript_aTables7_052522.csv"))
```
<br>
<br>
```{r Prevalence Difference Plots, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
PrevDiff$textY = -6.5
PrevDiff_m <- PrevDiff %>% mutate(LowerCL_l = ifelse(LowerCL < -.10, -.10, LowerCL), UpperCL_l = ifelse(UpperCL > .35, .35, UpperCL), 
                                  UpperCL_d = ifelse(UpperCL > .35, .35, NA))
#Creating Datasets for CI arrows for Black participants only (have to apply after doing facet wrap)
#Black UCL Logistic
# data.seglg<-data.frame(x=4, xend=4, y=19.4, yend = 30.0, Group="Black", model3="G2")
#Black UCL GBM
# data.seggbm<-data.frame(x=3, xend=3, y=15.0, yend = 30.0, Group="Black", model3="G6")
pd <- ggplot(PrevDiff_m, aes(x=Labels, y=Value*100, fill=model3)) + 
  geom_point(size = 10, alpha = 0.75, aes(fill=model3),colour="black", pch=21)+
  theme(aspect.ratio = 2) +
  geom_errorbar(aes(ymin=LowerCL_l*100, ymax=UpperCL_l*100),
                size=.8,    # Thinner lines
                width=.2,
                position=position_dodge(.9)) +
  labs(x="", y="Estimated Prevalence Difference (95% CI)") +
  ggtitle("Hypertension Prevalence Differences based on each weighting scheme") +
  scale_y_continuous(breaks=seq(-5,35,5), labels=scaleFUN, limit=c(-5,35),expand=c(0,0), minor_breaks =NULL) +
  theme_bw() +
  guides(fill=FALSE) +
  scale_fill_manual(values=c("G1"="white", "G2"="red1", "G3"="turquoise1","G4"="gold1","G6"="orchid1","G5"="black")) +
  theme_bw()+
  geom_text(aes(label=scaleFUN(Value*100)),hjust=.50, vjust=-1.25, size=6) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=17, color="black"), plot.title = element_text(hjust=0.5), axis.text.y=element_text(size=18, color="black")) +
  geom_hline(yintercept=0) + 
  scale_x_discrete(limits=rev(levels(PrevDiff$Labels))) +
  coord_flip() + 
  theme(panel.spacing= unit(3.0, "lines"))+
  theme(axis.text.y = element_text(hjust = 0)) + 
  #geom_segment(aes(x = 3, xend = 3, y = Value*100, yend = UpperCL_d*100), arrow = arrow(length = unit(0.5, "cm")))  +
  # geom_segment(aes(x = 2, xend = 2, y = Value*100, yend = UpperCL_d*100), arrow = arrow(length = unit(0.5, "cm"))) +
  facet_wrap(~ Group2) #+
# geom_segment(data=data.seglg, 
#              aes(x = x, xend = xend, y = y, yend = yend), inheret.aes=FALSE, arrow = arrow(length = unit(0.5, "cm"))) + 
# geom_segment(data=data.seggbm, 
#              aes(x = x, xend = xend, y = y, yend = yend), inheret.aes=FALSE, arrow = arrow(length = unit(0.5, "cm")))
pd2 <- pd + theme(strip.text = element_text(size=23),
                  plot.title = element_text(color="black", size=25, face="bold", vjust = 3.0),
                  axis.title.x = element_text(color="black", size=23, vjust=-3.0),
                  axis.title.y = element_text(color="black", size=16), 
                  plot.margin = margin(1,1,1,.1, "cm"), plot.background = element_rect(fill="white")
)
plot(pd2)
aspect_ratio <- 1.5
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/PD_052522.png'), plot=pd2, height=7,width = 10 * aspect_ratio )
```
<br>
<br>

##Prevalences
```{r Prev Data}
Prev <- results %>% filter(Statistic=='Prevalence' & Group!="Overall", Stdpop == "unstd")
scaleFUN <- function(x) sprintf("%.1f", x)
write.csv(Prev, file=paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Final graphics/Manuscript_aTables5_052522.csv"))

Prev2 <- results %>% filter(Statistic=='Prevalence' & Group!="Overall", Stdpop == "stdchis")
scaleFUN <- function(x) sprintf("%.1f", x)
write.csv(Prev2, file=paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Final graphics/Manuscript_aTables5b_052522.csv"))
```
<br>
<br>
```{r Prevalence Plots, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
Prev$textY = 43
p <- ggplot(Prev, aes(x=Labels, y=Value, fill=model3)) + 
  geom_point(size = 6, alpha = 0.75, aes(fill=model3),colour="black", pch=21) +
  theme(aspect.ratio = 2) +
  geom_errorbar(aes(ymin=LowerCL, ymax=UpperCL),
                size=.8,    # Thinner lines
                width=.2, 
                position=position_dodge(.9)) +
  labs(x="",y="Estimated Prevalence (95% CI)") +
  ggtitle("Estimated Hypertension Prevalence based on each weighting scheme") +
  scale_y_continuous(limit=c(30,90),expand=c(0,0),labels=scaleFUN, oob = rescale_none, minor_breaks = NULL) +
  guides(fill=FALSE) +
  scale_fill_manual(values=c("G1"="white", "G2"="red1", "G3"="turquoise1","G4"="gold1","G6"="orchid1","G5"="black")) +
  theme_bw() +
  geom_text(aes(label=scaleFUN(Value)),hjust=.50, vjust=-1.25, size=6) + 
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=17, color="black"), plot.title = element_text(hjust=0.5), axis.text.y=element_text(size=20, color="black")) +
  # geom_hline(yintercept=40) + # vertical line at 40--remove
  scale_x_discrete(limits=rev(levels(Prev$Labels))) +
  coord_flip() + 
  theme(panel.spacing= unit(3.0, "lines"))+
  theme(axis.text.y = element_text(hjust = 0)) + 
  facet_wrap(~ Group)
p2 <- p + theme(strip.text = element_text(size=23),
                plot.title = element_text(color="black", size=25, face="bold"),
                axis.title.x = element_text(color="black", size=23, vjust=-3.0),
                axis.title.y = element_text(color="black", size=16),
                plot.margin = margin(1,1,1,.1,"cm"), plot.background = element_rect(fill="white")
)
plot(p2)
aspect_ratio <- 1.5
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Prev_052522.png'), plot=p2, height=7,width = 10 * aspect_ratio )
```
<br>
<br>

#Areas of Common Support
In this section, we evaluate potential positivity violations using density plots showing propensity score overlap. The current graphs below show the distribution of the weights for each weighting scheme. They need to be updated with the propensity score instead of the weights.
```{r ACS Data}
density <- read.csv(paste0(path_to_box, "KD_bootstrapping/Scripts_18May2022/Output/weights_comb_short_0214222.csv")) %>% dplyr::select(-X)
```
<br>
<br>

##Logistic Propensity Balance
-make text larger (numeric values)
-more space between x-axis labels and x-axis numbering
-once all are plotted, then determine scale range
-consider knitting together three plots (stacked vertically) > all three should fit on one page, with room for title, space between, and footnotes

```{r Overall ACS Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
density$adclog[density$adc==0] <- " CHIS participant" 
density$adclog[density$adc==1] <- " ADC  participant"
density$adclog <- factor(density$adclog,levels = c(" ADC  participant"," CHIS participant"))
density$IP_2 <- density$IP_1*(4622757/856) #we are multiplying the propensity scores by the ratio of sample sizes for interpretability -- ERM note 1/21/2020: CHIS weighted sample size updated.
denlog<-ggplot(density, aes(x = IP_2, fill = adclog)) + geom_density(alpha = 0.5) + 
  labs(x="rescaled propensity score for ADC participation \nestimated from logistic regression", y="density")+
  scale_x_continuous(limit=c(0,20),expand=c(0,0), oob = rescale_none, minor_breaks = NULL) +
  scale_y_continuous(breaks=c(0.0,0.5,1.0,1.5,2.0), limit=c(0,2.0),expand=c(0,0), minor_breaks=NULL) +
  scale_fill_manual(values=c(" CHIS participant" ="grey88", " ADC  participant"="red1")) +
  geom_text (x=0, y=2.25, inherit.aes=FALSE, label="A.", check_overlap=TRUE, hjust=0, size=6) +
  #"Density Plot of Propensity Scores for ADC Participation \n estimated from logistic regression"
  coord_cartesian(clip = "off") +
  theme_bw()
denlog2 <- denlog + theme(strip.text = element_text(size=15),
                          plot.title = element_text(color="black", face="bold"),
                          axis.title.x = element_text(color="black", size=16, vjust=-1.5),
                          axis.text.x = element_text(size=12),
                          axis.title.y = element_text(color="black", size=16),
                          axis.text.y = element_text(size=12),
                          legend.title=element_blank(), legend.position = c(.85,.75), legend.text = element_text(size=14),
                          plot.margin = margin(4,1,1,.1,"cm"), plot.background = element_rect(fill="white")
)
plot(denlog2)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_Log_021422.png'), plot=denlog2, height=7,width = 8 * aspect_ratio  )
```

<br>
<br>

```{r Stratified ACS Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
density$adclog[density$adc==0] <- " CHIS participant" 
density$adclog[density$adc==1] <- " ADC  participant"
density$adclog <- factor(density$adclog,levels = c(" ADC  participant"," CHIS participant"))
density$IP_2 <- density$IP_1*(4622757/856) #we are multiplying the propensity scores by the ratio of sample sizes for interpretability -- ERM note 1/21/2020: CHIS weighted sample size updated.

plot_labels <- 
  data.frame(race = c("Black", "Latino", "White"), label = c("A. ", "", ""), 
             adclog = 1) %>% mutate_at("adclog", as.factor)

denlog_strat<-ggplot(density, aes(x = IP_2, fill = adclog)) + geom_density(alpha = 0.5) + 
  labs(x="stratified rescaled propensity score for ADC participation \nestimated from logistic regression", y="density")+
  scale_x_continuous(limit=c(0,20),expand=c(0,0), oob = rescale_none, minor_breaks = NULL) +
  # scale_y_continuous(breaks=c(0.0,0.5,1.0,1.5,2.0), limit=c(0,2.0),expand=c(0,0), minor_breaks=NULL) +
  scale_fill_manual(values=c(" CHIS participant" ="grey88", " ADC  participant"="red1")) +
  #"Density Plot of Propensity Scores for ADC Participation \n estimated from logistic regression"
  coord_cartesian(clip = "off") + 
  facet_grid(rows = vars(race), scales = "free") + theme_bw() + 
  geom_text(x = 0, y = 0.2, aes(label = label), data = plot_labels, 
            check_overlap = TRUE, hjust = 0, size = 6)

denlog2_strat <- denlog_strat + 
  theme(strip.text = element_text(size=15),
        plot.title = element_text(color="black", face="bold"),
        axis.title.x = element_text(color="black", size=16, vjust=-1.5),
        axis.text.x = element_text(size=12),
        axis.title.y = element_text(color="black", size=16),
        axis.text.y = element_text(size=12),
        legend.title=element_blank(), legend.position = c(.85,.90), legend.text = element_text(size=14),
        plot.margin = margin(4,1,1,.1,"cm"), plot.background = element_rect(fill="white"), 
        panel.spacing.y = unit(4, "mm")) 
plot(denlog2_strat)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_Log_021422_strat.png'), plot=denlog2_strat, height=7,width = 8 * aspect_ratio  )
```

<br>
<br>


##GBM Propensity Balance
```{r GBM ACS Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
density$adcgbm[density$adc==0] <- " CHIS participant" 
density$adcgbm[density$adc==1] <- " ADC  participant"
density$adcgbm <- factor(density$adcgbm,levels = c(" ADC  participant"," CHIS participant"))
density$pp2_ADC2 <- density$pp2_ADC*(4622757/856) #we are multiplying the propensity scores by the ratio of sample sizes for interpretability -- ERM note 1/21/2020: CHIS weighted sample size updated.
dengbm<-ggplot(density, aes(x = pp2_ADC2, fill = adcgbm)) + geom_density(alpha = 0.5) + 
  labs(x="rescaled propensity score for ADC participation \nestimated from GBM", y="density") +
  scale_x_continuous(limit=c(0,20),expand=c(0,0), oob = rescale_none, minor_breaks = NULL) +
  scale_y_continuous(breaks=c(0.0,0.5,1.0,1.5,2.0), limit=c(0,2.0),expand=c(0,0), minor_breaks=NULL) +
  scale_fill_manual(values=c(" CHIS participant" ="grey88", " ADC  participant"="orchid1")) +
  geom_text (x=0, y=2.25, inherit.aes=FALSE, label="B.", check_overlap=TRUE, hjust=0, size=6) +
  #"Density Plot of Propensity Scores for ADC Participation \n estimated from logistic regression"
  coord_cartesian(clip = "off") +
  theme_bw()
dengbm2 <- dengbm + theme(strip.text = element_text(size=15),
                          plot.title = element_text(color="black", face="bold"),
                          axis.title.x = element_text(color="black", size=16, vjust=-1.5),
                          axis.text.x = element_text(size=12),
                          axis.title.y = element_text(color="black", size=16),
                          axis.text.y = element_text(size=12),
                          legend.title=element_blank(), legend.position = c(.85,.75), legend.text = element_text(size=14),
                          plot.margin = margin(4,1,1,.1,"cm"), plot.background = element_rect(fill="white")
)
plot(dengbm2)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_GBM_021422.png'), plot=dengbm2, height=7,width = 8 * aspect_ratio  )
```
<br>
<br>

```{r Stratified GBM ACS Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
density$adcgbm[density$adc==0] <- " CHIS participant" 
density$adcgbm[density$adc==1] <- " ADC  participant"
density$adcgbm <- factor(density$adcgbm,levels = c(" ADC  participant"," CHIS participant"))
density$pp2_ADC2 <- density$pp2_ADC*(4622757/856) #we are multiplying the propensity scores by the ratio of sample sizes for interpretability -- ERM note 1/21/2020: CHIS weighted sample size updated.

plot_labels <- 
  data.frame(race = c("Black", "Latino", "White"), label = c("B. ", "", ""), 
             adcgbm = 1) %>% mutate_at("adcgbm", as.factor)

dengbm_strat<-ggplot(density, aes(x = pp2_ADC2, fill = adcgbm)) + geom_density(alpha = 0.5) + 
  labs(x="stratified rescaled propensity score for ADC participation \nestimated from GBM", y="density") +
  scale_x_continuous(limit=c(0,20),expand=c(0,0), oob = rescale_none, minor_breaks = NULL) +
  # scale_y_continuous(breaks=c(0.0,0.5,1.0,1.5,2.0), limit=c(0,2.0),expand=c(0,0), minor_breaks=NULL) +
  scale_fill_manual(values=c(" CHIS participant" ="grey88", " ADC  participant"="orchid1")) +
  #"Density Plot of Propensity Scores for ADC Participation \n estimated from logistic regression"
  coord_cartesian(clip = "off") + facet_grid(rows = vars(race), scales = "free") + theme_bw() + 
  geom_text(x = 0, y = 0.225, aes(label = label), data = plot_labels, 
            check_overlap = TRUE, hjust = 0, size = 6)

dengbm2_strat <- dengbm_strat + theme(strip.text = element_text(size=15),
                                      plot.title = element_text(color="black", face="bold"),
                                      axis.title.x = element_text(color="black", size=16, vjust=-1.5),
                                      axis.text.x = element_text(size=12),
                                      axis.title.y = element_text(color="black", size=16),
                                      axis.text.y = element_text(size=12),
                                      legend.title=element_blank(), legend.position = c(.85,.90), legend.text = element_text(size=14),
                                      plot.margin = margin(4,1,1,.1,"cm"), plot.background = element_rect(fill="white"), panel.spacing.y = unit(4, "mm")
)
plot(dengbm2_strat)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_GBM_021422_strat.png'), plot=dengbm2_strat, height=7,width = 8 * aspect_ratio  )
```

##super learner Propensity Balance
```{r SL ACS Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
density$adcsl[density$adc==0] <- " CHIS participant" 
density$adcsl[density$adc==1] <- " ADC  participant"
density$adcsl <- factor(density$adcsl,levels = c(" ADC  participant", " CHIS participant"))
density$pp_SL2 <- density$pp_SL*(4622757/856) #we are multiplying the propensity scores by the ratio of sample sizes for interpretability -- ERM note 1/21/2020: CHIS weighted sample size updated.
densl<-ggplot(density, aes(x = pp_SL2, fill = adcsl)) + geom_density(alpha = 0.5) + 
  labs(x="rescaled propensity score for ADC participation \nestimated from super learner", y="density") +
  scale_x_continuous(limit=c(0,20),expand=c(0,0), oob = rescale_none, minor_breaks = NULL) +
  scale_y_continuous(breaks=c(0.0,0.5,1.0,1.5,2.0), limit=c(0,2.0),expand=c(0,0), minor_breaks=NULL) +
  scale_fill_manual(values=c(" CHIS participant" ="grey88", " ADC  participant"="gold1")) +
  geom_text (x=0, y=2.25, inherit.aes=FALSE, label="C.", check_overlap=TRUE, hjust=0, size=6) +
  #"Density Plot of Propensity Scores for ADC Participation \n estimated from logistic regression"
  coord_cartesian(clip = "off") +
  theme_bw()
densl2 <- densl + theme(strip.text = element_text(size=15),
                        plot.title = element_text(color="black", face="bold"),
                        axis.title.x = element_text(color="black", size=16, vjust=-1.5),
                        axis.text.x = element_text(size=12),
                        axis.title.y = element_text(color="black", size=16),
                        axis.text.y = element_text(size=12),
                        legend.title=element_blank(), legend.position = c(.85,.75), legend.text = element_text(size=14),
                        plot.margin = margin(4,1,1,.1,"cm"), plot.background = element_rect(fill="white")
)
plot(densl2)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_SL_021422.png'), plot=densl2, height=7,width = 8 * aspect_ratio  )
##ADD Footnote at the bottom of all three that we have trimmed the scale from 0-20!!
```

```{r stratified SL ACS Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
density$adcsl[density$adc==0] <- " CHIS participant" 
density$adcsl[density$adc==1] <- " ADC  participant"
density$adcsl <- factor(density$adcsl,levels = c(" ADC  participant", " CHIS participant"))
density$pp_SL2 <- density$pp_SL*(4622757/856) #we are multiplying the propensity scores by the ratio of sample sizes for interpretability -- ERM note 1/21/2020: CHIS weighted sample size updated.

plot_labels <- 
  data.frame(race = c("Black", "Latino", "White"), label = c("C. ", "", ""), 
             adcsl = 1) %>% mutate_at("adcsl", as.factor)

densl_strat<-ggplot(density, aes(x = pp_SL2, fill = adcsl)) + geom_density(alpha = 0.5) + 
  labs(x="stratified rescaled propensity score for ADC participation \nestimated from super learner", y="density") +
  scale_x_continuous(limit=c(0,20),expand=c(0,0), oob = rescale_none, minor_breaks = NULL) +
  # scale_y_continuous(breaks=c(0.0,0.5,1.0,1.5,2.0), limit=c(0,2.0),expand=c(0,0), minor_breaks=NULL) +
  scale_fill_manual(values=c(" CHIS participant" ="grey88", " ADC  participant"="gold1")) +
  #"Density Plot of Propensity Scores for ADC Participation \n estimated from logistic regression"
  coord_cartesian(clip = "off") + facet_grid(rows = vars(race), scales = "free") + theme_bw() + 
  geom_text(x = 0, y = 0.19, aes(label = label), data = plot_labels, 
            check_overlap = TRUE, hjust = 0, size = 6)

densl2_strat <- densl_strat + theme(strip.text = element_text(size=15),
                                    plot.title = element_text(color="black", face="bold"),
                                    axis.title.x = element_text(color="black", size=16, vjust=-1.5),
                                    axis.text.x = element_text(size=12),
                                    axis.title.y = element_text(color="black", size=16),
                                    axis.text.y = element_text(size=12),
                                    legend.title=element_blank(), legend.position = c(.85,.90), legend.text = element_text(size=14),
                                    plot.margin = margin(4,1,1,.1,"cm"), plot.background = element_rect(fill="white"), panel.spacing.y = unit(4, "mm")
)
plot(densl2_strat)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_SL_021422_strat.png'), plot=densl2_strat, height=7,width = 8 * aspect_ratio  )
##ADD Footnote at the bottom of all three that we have trimmed the scale from 0-20!!
```


```{r Comb Den Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
g <- grid.arrange(denlog2,dengbm2,densl2,ncol=1)
plot(g)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_ALL_021422.png'), plot=g, height=12,width = 6 * aspect_ratio  )
```
<br>
<br>

```{r stratified Comb Den Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
g <- grid.arrange(denlog2_strat,dengbm2_strat,densl2_strat,ncol=1)
plot(g)
aspect_ratio <- 1.25
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/Den_ALL_021422_strat.png'), plot=g, height=20,width = 8 * aspect_ratio  )
```
<br>
<br>
#Covariate Balance Plots

```{r Cov Balance Plot, echo=FALSE, fig.align="center", out.width="75%", out.height="75%"}
all_paths <- 
  list.files(path = paste0(path_to_box,
                           "KD_bootstrapping/Scripts_18May2022/Output"), 
             full.names = TRUE, pattern = "*.csv")

results_paths <- all_paths[str_detect(all_paths, "SEseize_FULL")]

df1 <- do.call(rbind, lapply(results_paths, read_csv)) %>% dplyr::select(-1)

df1$Group[df1$Group=="GBM"] <- "sIOSW,\nalgorithm: GBM" 
df1$Group[df1$Group=="LOGSLPT2"] <- "sIOSW,\nalgorithm: logistic regression" 
df1$Group[df1$Group=="RAKED"] <- "Raking weights" 
df1$Group[df1$Group=="SL"] <- "sIOSW,\nalgorithm: super learner" 
df1$Group2 <- factor(df1$Group, levels = c("Raking weights", "sIOSW,\nalgorithm: logistic regression" ,"sIOSW,\nalgorithm: GBM" , "sIOSW,\nalgorithm: super learner"))
df1$Covariate <- 
  factor(df1$Covariate, 
         levels = df1 %>% filter(Model == "Unweighted", race_label == "all") %>%
           group_by(Covariate) %>% slice_head(n = 1) %>% arrange(desc(Effect_Size)) %>% dplyr::select(Covariate) %>% unlist())

#combined plot
CVB <- ggplot(df1 %>% filter(race_label == "all"), aes(x=Covariate, y=-1*Effect_Size), group=Model) + 
  facet_wrap(~Group2, nrow = 1) + 
  geom_hline(yintercept = 0, size = 1) +
  geom_point(size=3, aes(colour=factor(Model), shape=factor(Model), fill=factor(Model))) +
  ylab("Standardized mean difference") +
  # ggtitle("Covariate Balance") + 
  scale_y_continuous(breaks=round(seq(-0.6, 0.8, by = 0.2), 2), 
                     limit=c(-0.6, 0.8), minor_breaks=NULL) +
  scale_shape_manual(values=c("LOGSLPT2"=24,"GBM"=24,"SL"=24,"RAKED"=24,"Unweighted"=1)) +
  scale_colour_manual(values=c("black","black","black","black","black")) +
  scale_fill_manual(values=c("Unweighted"="white", "LOGSLPT2"="red1","GBM"="orchid1", "SL"="gold1", "RAKED"="turquoise1")) + 
  theme_bw() +
  theme(axis.title.y=element_blank()) + 
  theme(legend.position = "none") + 
  theme(aspect.ratio = 5/3) +
  coord_flip()
CVB2 <- CVB + theme(strip.text = element_text(size=18),
                    axis.title.x = element_text(color="black", size=20, vjust=-3.0),
                    axis.text.x = element_text(size=16),
                    axis.text.y = element_text(size=16),
                    plot.margin = margin(.25,.25,.25,.25,"cm"), plot.background = element_rect(fill="white"))
plot(CVB2)
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/CovBalance_FULL_021422.png'), plot=CVB2, width = 18, height=8, dpi=800  )

#stratified plot
CVB_strat <- ggplot(df1 %>% filter(!race_label == "all"), aes(x=Covariate, y=-1*Effect_Size), group=Model) + 
  facet_grid(rows = vars(race_label), cols = vars(Group2)) + 
  geom_hline(yintercept = 0, size = 1) +
  geom_point(size=3, aes(colour=factor(Model), shape=factor(Model), fill=factor(Model))) +
  ylab("Standardized mean difference") +
  scale_y_continuous(breaks=round(seq(-0.6, 0.8, by = 0.2), 2), 
                     limit=c(-0.6, 0.8), minor_breaks=NULL) +
  scale_shape_manual(values=c("LOGSLPT2"=24,"GBM"=24,"SL"=24,"RAKED"=24,"Unweighted"=1)) +
  scale_colour_manual(values=c("black","black","black","black","black")) +
  scale_fill_manual(values=c("Unweighted"="white", "LOGSLPT2"="red1","GBM"="orchid1", "SL"="gold1", "RAKED"="turquoise1")) + 
  theme_bw() +
  theme(axis.title.y=element_blank()) + 
  theme(legend.position = "none") + 
  theme(aspect.ratio = 5/3) +
  coord_flip()
CVB2_strat <- CVB_strat + theme(strip.text = element_text(size=18),
                                axis.title.x = element_text(color="black", size=20, vjust=-3.0),
                                axis.text.x = element_text(size=16),
                                axis.text.y = element_text(size=16),
                                plot.margin = margin(.5,.5,.5,.5,"cm"), plot.background = element_rect(fill="white"))
plot(CVB2_strat)
ggsave(filename=paste0(path_to_box, 'KD_bootstrapping/Scripts_18May2022/Final graphics/PLOTS/CovBalance_FULL_021422_strat.png'), plot=CVB2_strat, width = 25, height=20, dpi=800  )
```
